---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rotfornip

<!-- badges: start -->
<!-- badges: end -->

The goal of rotfornip is to extend parsnip to handle rotationforest models as an engine for rand_forest()

## Installation

This package isn't on CRAN - and won't be, unless someone submits a rotationforest implementation there that I wrap.

The development version from [GitHub](https://github.com/) can be installed with:

``` r
# install.packages("devtools")
devtools::install_github("mananshah99/rotationforest")
devtools::install_github("mattsq/rotfornip")
```
## Example

Here's how you'd use it:

```{r example}
library(tidymodels)
library(rotationForest)
library(rotfornip)

```

Here we'll use the two_class_dat example model from modeldata

```{r cars}
#
 data("two_class_dat", package = "modeldata")
 set.seed(4622)
 example_split <- initial_split(two_class_dat, prop = 0.7)
 example_train <- training(example_split)
 example_test  <-  testing(example_split)
 bs_train <- bootstraps(example_train)

```

A simple fit/predict example:

```{r simple}

 model <- rand_forest(trees = 100, mtry = 1, mode = "classification") %>%
   set_engine(engine = "rotationForest")
 rot_for_fit <- model %>%
   fit(Class ~ ., data =  example_train)
 predict(rot_for_fit, new_data = example_train)

```  

A more complex example:

```{r complex}

 recipe_rot <- recipe(Class ~ ., data = example_train) %>%
   step_normalize(all_predictors())
 model_grid <- rand_forest(trees = tune(), mtry = tune(), mode = "classification") %>%
   set_engine(engine = "rotationForest")
 wf <- workflow() %>%
   add_recipe(recipe_rot) %>%
   add_model(model_grid)
 grid_rot <- grid_random(mtry(range = c(1,2)), trees(), size = 3)

grid_results <- tune_grid(wf, resamples = bs_train, grid = grid_rot)

collect_metrics(grid_results)

```

